---
title: "Assignment 1"
subtitle: "STATS 220 Semester One 2022"
author: "Dennis Nieuwenhuizen - dnie495"
date: '2022-03-19'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(magick)
library(tidyverse)
```

## GitHub repository information

[Github Repository](https://github.com/shakenrobot/stats220)

This stats220 github repository includes Part A and Part B of my Assignment 1.

It has a README.md file explaining the repository. It has a link to the Github Pages of Part A's section

The index.md and my_meme.png are linked to Part A of the assignment which tackles creation of a meme in R. 

The other index.Rmd and index.html files are linked to Part B of the assignment which tackles creation a gif in R.

## Animated GIF creation

For the gif creation I have decided to make a gif of a stick man doing a flip. 

It has 12 frames in total.

The first gif has no border and the second has a border. The border was used during gif creation to format the offset of the stick man.


```{r}
# gif creation

#load in stick_man image I have created
stick_man <- image_read("https://i.imgur.com/4IlQDMz.png") %>% image_scale(100)



# create the 12 frames for the gif
frame1 <- image_blank(color = "#FFFFFF", width = 500, height = 500)  %>%
  image_scale(500) %>% image_composite(stick_man, offset = "+0+360")

frame2 <- image_blank(color = "#FFFFFF", width = 500, height = 500)  %>%
  image_scale(500) %>% image_composite(stick_man, offset = "+40+360")

#create the rotations of the stick_man for following frames (3 - 8)
stick_man_flip_1 <- image_rotate(stick_man, 60)
stick_man_flip_2 <- image_rotate(stick_man, 120)
stick_man_flip_3 <- image_rotate(stick_man, 180)
stick_man_flip_4 <- image_rotate(stick_man, 240)
stick_man_flip_5 <- image_rotate(stick_man, 300)
stick_man_flip_6 <- image_rotate(stick_man, 360)

frame3 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_scale(500) %>% image_composite(stick_man_flip_1, offset = "+80+300")

frame4 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_scale(500) %>% image_composite(stick_man_flip_2, offset = "+120+240")

frame5 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_scale(500) %>% image_composite(stick_man_flip_3, offset = "+160+180")

frame6 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_scale(500) %>% image_composite(stick_man_flip_4, offset = "+200+240")

frame7 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_scale(500) %>% image_composite(stick_man_flip_5, offset = "+240+300")

frame8 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_scale(500) %>% image_composite(stick_man_flip_6, offset = "+280+360")

frame9 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_scale(500) %>% image_composite(stick_man, offset = "+320+360")

frame10 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_scale(500) %>% image_composite(stick_man, offset = "+360+360")

#adding nice flip! text
frame11 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_annotate(text = "nice flip!", size = 100, gravity = "center")

frame12 <- image_blank(color = "#FFFFFF", width = 500, height = 500) %>%
  image_annotate(text = "nice flip!", size = 100, gravity = "center")
  


# putting the frames in order
frames <- c(frame1, frame2, frame3, frame4, frame5, frame6, frame7, frame8, frame9, frame10, frame11, frame12)

# create the final animation
image_animate(frames)

# write gif to a file 
image_write(image_animate(frames), path = "flip_gif.gif")

# animation with border (used in gif creation)
frames <- image_border(frames, "black", "1x1")

image_animate(frames, fps = 5)

```

#### css

```{css}
a:link, a:visited, a:hover, a:active {
  color: #FFFF33
}
body {
  background-color: #D2B4DE ;
  font-family: "Verdana"
}



```
## Learning reflection

The main idea I learnt from module 1 was how to combine images together into different formats. It can be quite fun to create things you want to make with your own ideas/choices with code.

Another key learning point would be commenting my code. After focusing more on using comments in Part B I noticed it was a lot easier to skim through code and understand where it fits together. In future assignments and with other coding languages I will definitely focus more on adding comments into projects.

In relation to data technologies, I'm most interested in how I can use technologies to display large/big data in a visual friendly way. Having large data/datasets and finding the key information you need from them seems fun to do and interesting.
